### 2022-03-07 src/text/3-applications.tex
Update 3-applications.tex
reorder applications sections

Each application example is a notebook in the online material: We could have
one analysis as Python scripts instead of notebook in the online material. At
the start of this section, point to gammapy-paper repo on Github and say that
there’s a Binder where people can try the examples online.

TODO: mention other application examples (joint Crab paper, HESS validation
paper, HGPS, ...) here or in a subsection "other applications" at the end of
this section?

\subsection{Source detection}
\label{ssec:source-detection}

@@

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}

>>>>

Show some typical and advanced science cases, and refer to published papers

\subsection{Computing Flux points and significance maps}
\label{ssec:1D-3D-analysis}
\input{3.1-std-analysis}

- standard 1D and 3D analysis

@@

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3.2-temporal}
lightcurves and temporal models

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-models-analysis}
\todo{Cosimo}
\begin{figure*}[t]
(added section in the text requesting multi-insturment figure)

\end{figure}

\subsection{Population studies}
\label{ssec:population-studies}
\todo{Quentin Remy}

Talk about simulations here? Or open a new section
